Embedding Intuitionistic into Classical Logic

### 2022-07-16 CSL/lipics-v2021-EIICL.tex
Typos, Example 34

Constructive mathematics refers to a flavour of mathematics in which the existence of an object can only be established by explicit construction, as opposed to classical mathematics where existence can be shown implicitly, e.g. by assuming non-existence and deriving a contradiction.
The formalism usually associated with constructive mathematics is intuitionistic logic, which essentially differentiates itself from classical logic by the fact that the law of excluded middle $A\vee\neg A$ and the double negation shift $\forall x\neg\neg P(x)\to\neg\neg\forall xP(x)$ are not valid.
Besides philosophical considerations, most prominently advocated by Brouwer~\cite{brouwer1907over} and Bishop~\cite{bishop1967foundations}, there is a particul<ar motivation for studying constructive mathematics from the perspective of computer science in that proofs in  intuitionistic logic directly correspond to computer programs --- as expressed in famous Curry-Howard correspondence~\cite{howard1980formulae}.

The interest in intuitionistic logic has lead to the development of a number of automated theorem proving systems for propositional as well as for predicate logic and a collection of benchmarks problems (see e.g. the
ILTP library website~\cite{iltp}).
However, progress in automated theorem proving for intuitionistic logic has been slow, whereas reasoners for classical logic have made tremendous progress, see e.g. the TPTP~\cite{casc} and SAT~\cite{satc} competitions.
%, e.g., the first-order provers~\cite{kovacs2013first, schulz2002brainiac, korovin2008iprover}
%Comparing benchmarks for classical and intuitionistic automated theorem proving, e.g. TPTP~\cite{casc} and , we see that classical provers currently have a far better success rate. Furthermore all the most popular first-order utilize classical logic.
This difference can be partially explained by fundamental differences between the logics.
First of all, determining intuitionistic validity is computationally harder, i.e. in the propositional case intuitionistic validity is \verb+PSPACE+-complete~\cite{statman1979intuitionistic} whereas classical validity is \verb+coNP+-complete~\cite{cook1971complexity}.
A further advantage of classical logic is the existence of calculi that are particularly suitable for automation such as superposition~\cite{bachmair2001resolution}, which rely on the existence of convenient normal forms such as CNF, and the duality between validity and satisfiability, i.e. to show the validity of a formula it suffices to show the unsatisfiability of the negated formula.
While some (albeit more complex) normal forms also exist  for intuitionistic logic, crucially the duality between validity and satisfiability of the negation does not hold.
Therefore most dedicated intuitionistic theorem provers~\cite{mclaughlin2009efficient, tammet1996resolution} use the naive inverse method, i.e. directly search for a cut-free proof by applying the rules from some proof calculus inversely, enhanced by search strategies such as focussing and polarization. This approach generally leads to a much more complex search and is therefore difficult to implement efficiently.
Finally, we add that in contrast to intuitionistic provers a tremendous amount of work has been put into optimizing provers for classical logic, in particular for the propositional case, i.e. SAT-solvers.

@@

\begin{theorem}
For every propositional formula $\varphi$ there effectively are an atom $P$ and a set of $\mathcal S$ of formulas (over an extended set of propositions) of one of the forms\\
$\text{ \hspace{1cm}} A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C), (A\vee B)\to C, (A\to B)\to C,$\\
for atomic $A, B, C$, such that $\varphi$ is intuitionistically valid if and only if $\bigwedge\mathcal S\to P$ is intuitionistically valid. The time complexity of the transformation is linear in the input size.
\end{theorem}

The main transformation then proceeds in three steps:
%
1) We encode as a first-order sentence that the considered formula holds for every Kripke frame.
Since Kripke frames for propositional logic over a fixed alphabet of propositional variables form a first-order theory this step is rather straightforward.
%
2) Next we eliminate some quantifiers via Herbrandization. The only quantifiers eliminated occur in formulas derived from formulas of type $(A\to B)\to C$.
%
3) We can then argue that if there is a counter-model for the resulting formula then there is a counter-model with a certain Kripke frame of bounded size completely determined by the number of formulas of type $(A\to B)\to C$.
This allows us to eliminate the remaining quantifiers by simply enumerating the worlds in that Kripke model.

@@

\begin{theorem}
\label{thm:reduction-propositional}
	Let $\mathcal S$ be as above. Let $\mathcal F_\to\subseteq\mathcal S$ denote formulas $\psi$ of the form $(A\to B)\to C$ and $\Lambda$ denote the set of sequences without repetition over $\mathcal F_\to$. For each atom $A$ and $k\in\Lambda$ consider a new atom $A^k$. Obtain $\mathcal S^\#$ by including the following formulas:
	\begin{itemize}
		\item $A^k\to A^{k\psi}$ for each atom $A$ occurring in $\mathcal S$, $k\in\Lambda$ and $\psi\in\mathcal F_\to$ not occurring in $k$.
		\item $A^k\to (B^k\circ C^k)$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^k\circ B^k)\to C^k$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^{k\psi}\to B^{k\psi})\to C^k$ for $\psi = (A\to B)\to C\in\mathcal S$, $k\in\Lambda$ if $\psi$ does not occurr in $k$.
	\end{itemize}
Then, $\bigwedge S\to P$ is intuitionistically valid iff $\bigwedge S^\#\to P^\epsilon$ is classically valid, where $\epsilon$ denotes the empty sequence. The size of $\mathcal S^\#$ is in $\mathcal O(|\mathcal S|\cdot2^{|\mathcal F_\to|\cdot\log(|\mathcal F_\to|)})$. Futhermore, there is an effective procedure for translating counter-models between the sentences.
\end{theorem}

@@

\begin{theorem}
	Let $\mathcal S$ be as above. There is an effective procedure that produces a QBF $\varphi^Q$ of size $\mathcal O(|\mathcal S|\cdot|\mathcal F_\to| + |\mathcal F_\to|^3)$ with $2\cdot |\mathcal F_\to|-1$ quantifier alternations such that $\varphi$ is intuitionistically valid if and only if $\varphi^Q$ is not satisfiable. For fixed $N\in\mathbb N$, deciding intuitionistic validity for formulas $\bigwedge \mathcal S\to P$ where $\mathcal S$ is as above and $|\mathcal F_\to| = N$ is therefore in $\Sigma_{2N-1}$.
\end{theorem}

@@

We then move to the first-order case. Here the construction is a bit more involved but the underlying approach is the same.
Again we first perform a Tseytin-like transformation.
Here the non-classical content is encapsulated by formulas of type $(A\to B)\to C$ and $\forall xA\to B$.
The details of this translation are given in Section~\ref{section:tseytin}.
We then proceed similarly to the propositional case.
Note however that one difficulty arises from the fact that our (classical) domain will now contain on the one hand worlds in the Kripke frame but on the other hand also proper domain elements.
We resolve this apparent conflict by introducing a special binary predicate $E$, inspired by~\cite{iemhoff2010eskolemization}, encoding which domain elements exists at which world.
In particular $E(x, u)$ entails that $x$ represents a domain element and $u$ a world.
The main transformation then again proceeds in three steps:
Step 1) and 2) are analogous to the propositional case.
The real difference arises in step 3):
While we can also establish the existence of a canonic counter-model whose size only depends on formulas of type $(A\to B)\to C$ and $\forall xA\to B$, the size of this counter-model is countably infinite in general.
This is not surprising since certain intuitionistically invalid formulas like the double negation shift $\forall x\neg\neg A(x)\to \neg\neg\forall x A(x)$ don't have finite counter-models.
Therefore we are not able to eliminate the $\forall$-quantifiers associated with the Kripke semantics.
However since our translation targets first-order logic, we believe that the introduction of these quantifiers is acceptable.
%
Summarizing, we obtain the following result:

@@

\begin{definition}
A $\Sigma$-\emph{Kripke structure} $\mathcal{K}$ is a partially ordered set $W$, called the Kripke \emph{frame}, and a family of $\Sigma$-structures $(\mathcal{M}_w)_{w\in W}$ such that for $u\leq w$ we have $M_u\subseteq M_w$, $f^{I_w}|_{M_u} = f^{I_u}$.\footnote{Here $f|_M$ denotes the restriction of $f$ to $M$} and $R^{I_w}|_{M_u} = R^{I_u}$.
	Then we define a model relation between worlds $u\in W$ and variable assignments $v$ (targeting $M_u$) and formulas $\varphi$ as follows:
	\begin{itemize}
		\item $u, v\not\models\bot$, $u, v\models R(t_1,\dots,t_n)$ iff $\mathcal M_u, v\models R(t_1,\dots,t_n)$, $u, v\models s = t$ iff $s^{I_u, v} = t^{I_u, v}$.
		\item $u, v\models \varphi\wedge \psi$ iff $u, v\models\varphi$ and $u, v\models\psi$, $u, v\models \varphi\vee\psi$ iff $u, v\models\varphi$ or $u, v\models\psi$.
		\item $u, v\models \varphi\to\psi$ iff for every $w\geq u$ we have $w, v\not\models\varphi$ or $w, v\models\psi$.
		\item $u, v\models\exists x\varphi$ iff there exists $m\in M_u$ such that $u, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $u, v\models\forall x\varphi$ iff for every $w\geq u$ and $m\in M_w$ we have $w, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\mathcal{K}$ satisfies $\varphi$ if $u, v\models\varphi$ holds for every world $u$ and variable assignment $v$. $\varphi$ is valid if it is satisfied by every Kripke structure.
$\varphi$ is valid for some frame (write $W\models\varphi$) if it is satisfied in every Krike structure with that frame. We denote the set of valid formulas with \emph{IQC} (Intuitionistic Quantified Calculus).
\end{definition}
In addition to the propositional tautologies there are now sentences involving quantifiers which are classically valid but not intuitionistically, e.g., $\neg\forall x A(x)\to \exists x \neg A(x)$.
Analogous remarks with regard to validity and satisfiability hold as in the propositional case.

@@

An important step in the embedding will be the elimination of quantifiers via Herbrandization.
In this process we introduce fresh variables and add additional function symbols to the signature.
A fresh variable is any variable that does not occur in any of the considered formulas.
Whenever we add function symbol we implicitly extend the signature by some not previously contained symbol.

@@

\begin{definition}
	Let $\varphi$ be a propositional formula. Define $\varphi^{u}$ inductively as follows:
	\begin{itemize}
		\item $A^{u} = A(u)$ for every propositional variable $A$.
		\item $\bot^u = \bot$.
		\item $(\varphi\circ\psi)^u = \varphi^u\circ\psi^u$ for $\circ\in\{\wedge, \vee\}$.
		\item $(\varphi\to \psi)^u = \forall w(u\preceq w\to\varphi^{w}\to\psi^{w})$ where $w$ is some new variable.
	\end{itemize}
	Let $K(\varphi)$ encode the Kripke semantics, i.e.
	$$K(\varphi) = \text{\normalfont PartialOrder}(\preceq)\wedge\forall u\forall w(u\preceq w\to \text{\normalfont Persistent}(u, w))$$
	with e.g.
	\begin{align*}
		\text{\normalfont PartialOrder}(\preceq) =&\:\forall u(u\preceq u)\wedge\forall u\forall w(u\preceq w\to w\preceq u\to u = w)\wedge\\&\:\forall u\forall v\forall w(u\preceq v\to v\preceq w\to u\preceq w)\\
		\text{\normalfont Persistent}(u, w)=&\:\bigwedge \{A(u)\to A(w))\:|\: \text{ $A$ is a propositional variable that occurs in $\varphi$}\}
	\end{align*}
	Then define
	$$\varphi^{C} = K(\varphi)\to \varphi^{u}$$
	where $u$ is some free variable.
\end{definition}

@@

\begin{lemma}
	$\bigwedge S^+(\varphi)\wedge P_\varphi\to\varphi$, $\bigwedge S^-(\varphi)\wedge \varphi\to P_\varphi$ hold classically and intuitionistically.
\end{lemma}

@@

\begin{lemma}\label{thm:struct2}
	For every structure $\mathcal M$,
	$\mathcal M\models \varphi$ if and only if $S(\mathcal M, \varphi)\models P_\varphi$.
\end{lemma}

Then from the previous three Lemmas we get:

@@

Recall that since $\varphi$ is quantifier-free each formula $\psi\in\mathcal S^-(\varphi)$ is of one of the forms
$$A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C), (A\vee B)\to C, (A\to B)\to C,$$
where we can treat $A\to B$ as a special case $A\to (B\wedge B)$. We then apply the transformation to CQC, leading to a formula
$$\varphi'' = K(\varphi')\to\bigwedge  \mathcal S\to P_\varphi(u),$$
where $u$ is some new free variable and each $\psi\in\mathcal S$ is of one of the forms
$$\begin{matrix}
	\forall k(u\preceq k\to A(k)\to (B(k)\wedge C(k)))\indent  \forall k(u\preceq k\to (A(k)\wedge (B(k))\to C(k)))\\
	\forall k(u\preceq k\to A(k)\to (B(k)\vee C(k)))\indent \forall k(u\preceq k\to (A(k)\vee B(k))\to C(k))\\
	\forall k(u\preceq k\to (\forall l(k\preceq l \to A(l)\to B(l))\to C(k))),
\end{matrix}$$
with each $P(x)$ possibly being $\bot$. Applying Herbrandization we obtain a formula
$$\varphi''' = K(\varphi')\to \bigwedge \mathcal S'\to P_\varphi(s),$$
where $s$ is some new constant term and each $\psi\in\mathcal S'$ is of one of the forms
$$\begin{matrix}
	\forall k(s\preceq k\to A(k)\to (B(k)\wedge C(k)))\indent \forall k(s\preceq k\to (A(k)\wedge (B(k))\to C(k)))\\
	\forall k(s\preceq k\to A(k)\to (B(k)\vee C(k)))\indent \forall k(s\preceq k\to (A(k)\vee (B(k))\to C(k)))\\
	\forall k(s\preceq k\to (k\preceq f_\psi(k) \to A(f_\psi(k))\to B(f_\psi(k)))\to C(k)),\\
\end{matrix}$$
and $f_\psi$ is a new function symbol for each introduced formula of that form. Now if $(M, I)$ is a counter-model, then we have a counter-model $(M',I')$ where $M' = \{m\in M|s\preceq m\}$ and
$f_\psi^{I'}(u) = f^I_\psi(u) \text{ iff $u\preceq f^{I}_\psi(u)$, and $f_\psi^{I'}(u) = u,$ else.}$ That is, where $s$ is the least element and the $f_\psi$ increase their argument. Therefore instead of $\varphi'''$ we may consider a formula $$\varphi^\circ = \forall k(s\preceq k)\to \bigwedge\{\forall k(k\preceq f_\psi(k))\:|\:\psi\in\mathcal F_\to\}\to K(\varphi')\to \bigwedge \mathcal S^\circ\to P_\varphi(s)$$ where each formula $\psi\in\mathcal S^\circ$ is of one of the forms
$$\begin{matrix}
	\forall k(A(k)\to (B(k)\wedge C(k)))\indent\forall k((A(k)\wedge B(k))\to C(k))\\
	\forall k(A(k)\to (B(k)\vee C(k)))\indent\forall k((A(k)\vee B_\psi(k))\to C(k))\\
	\forall k((A(f_\psi(k))\to B(f_\psi(k)))\to C(k)),
\end{matrix}$$
and $\mathcal F_\to$ denotes the set of formulas of the last kind.

@@

So we know that $\varphi^\circ$ is valid iff it is valid for structures that have as a domain the sequences without repetition over $\mathcal F_\to$, ordered by the prefix-relation and $$s^I = \epsilon, f_\psi^I(x) = \begin{cases}
	x, &\text{ if $\psi$ occurs in $x$,}\\
	x\psi, &\text{ otherwise.}
\end{cases}$$
Now we can replace every $\forall$-quantifier by enumerating all the ground terms, and then replace all distinct ground instances of relations by new propositional variables yielding a CPC formula. This gives us the translation stated in Theorem~\ref{thm:reduction-propositional}.
%\begin{theorem}
%	$\bigwedge\mathcal S\to P$ is intuitionistically valid iff $\bigwedge\mathcal S^\#\to P^\emptyset$ is classically valid.
%\end{theorem}

>>>>

Constructive mathematics refers to a flavour of mathematics in which the existence of an object can only be established by explicit construction, as opposed to classical mathematics where existence can be shown implicitly, e.g. by assuming non-existence and deriving a contradiction.
The formalism usually associated with constructive mathematics is intuitionistic logic, which essentially differentiates itself from classical logic by the fact that the law of excluded middle $A\vee\neg A$ and the double negation shift $\forall x\neg\neg P(x)\to\neg\neg\forall xP(x)$ are not valid.
Besides philosophical considerations, most prominently advocated by Brouwer~\cite{brouwer1907over} and Bishop~\cite{bishop1967foundations}, there is a particular motivation for studying constructive mathematics from the perspective of computer science in that proofs in  intuitionistic logic directly correspond to computer programs --- as expressed in the Curry-Howard correspondence~\cite{howard1980formulae}.

The interest in intuitionistic logic has lead to the development of a number of automated theorem proving systems for propositional as well as for predicate logic and a collection of benchmark problems (see e.g. the
ILTP library website~\cite{iltp}).
However, progress in automated theorem proving for intuitionistic logic has been slow, whereas reasoners for classical logic have made tremendous progress, see e.g. the TPTP~\cite{casc} and SAT~\cite{satc} competitions.
%, e.g., the first-order provers~\cite{kovacs2013first, schulz2002brainiac, korovin2008iprover}
%Comparing benchmarks for classical and intuitionistic automated theorem proving, e.g. TPTP~\cite{casc} and , we see that classical provers currently have a far better success rate. Furthermore all the most popular first-order utilize classical logic.
This difference can be partially explained by fundamental differences between the logics.
First of all, determining intuitionistic validity is computationally harder, i.e. in the propositional case intuitionistic validity is \verb+PSPACE+-complete~\cite{statman1979intuitionistic} whereas classical validity is \verb+coNP+-complete~\cite{cook1971complexity}.
A further advantage of classical logic is the existence of calculi that are particularly suitable for automation such as superposition~\cite{bachmair2001resolution}, which rely on the existence of convenient normal forms such as CNF, and the duality between validity and satisfiability, i.e. to show the validity of a formula it suffices to show the unsatisfiability of the negated formula.
While some (albeit more complex) normal forms also exist  for intuitionistic logic, crucially the duality between validity and satisfiability of the negation does not hold.
Therefore most dedicated intuitionistic theorem provers~\cite{mclaughlin2009efficient, tammet1996resolution} use the naive inverse method, i.e. directly search for a cut-free proof by applying the rules from some proof calculus inversely, enhanced by search strategies such as focussing and polarization. This approach generally leads to a much more complex search and is therefore difficult to implement efficiently.
Finally, we add that in contrast to intuitionistic provers a tremendous amount of work has been put into optimizing provers for classical logic, in particular for the propositional case, i.e. SAT-solvers.

@@

\begin{theorem}\label{thm:Tseytin}
For every propositional formula $\varphi$ there effectively are an atom $P$ and a set of $\mathcal S$ of formulas (over an extended set of propositions) of one of the forms\\
$\text{ \hspace{1cm}} A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C), (A\vee B)\to C, (A\to B)\to C,$\\
for atomic $A, B, C$, such that $\varphi$ is intuitionistically valid if and only if $\bigwedge\mathcal S\to P$ is intuitionistically valid. The time complexity of the transformation is linear in the input size.
\end{theorem}

The main transformation then proceeds in three steps:
%
1) We encode as a first-order sentence that the considered formula holds for every Kripke frame.
Since Kripke frames for propositional logic over a fixed alphabet of propositional variables form a first-order theory this step is rather straightforward.
%
2) Next we eliminate some quantifiers via Herbrandization. The only quantifiers eliminated occur in formulas derived from formulas of type $(A\to B)\to C$.
%
3) We can then argue that if there is a counter-model for the resulting formula then there is a counter-model with a certain Kripke frame of bounded size completely determined by the number of formulas of type $(A\to B)\to C$.
This allows us to eliminate the remaining quantifiers by simply enumerating the worlds in that Kripke frame.

@@

\begin{theorem}
\label{thm:reduction-propositional}
	Let $\mathcal S$ be as in Theorem~\ref{thm:Tseytin} and $\mathcal F_\to\subseteq\mathcal S$ denote the subset of formulas of the form $(A\to B)\to C$ and $\Lambda$ denote the set of sequences without repetition over $\mathcal F_\to$. For each atom $A$ and $k\in\Lambda$ consider a new atom $A^k$. Obtain $\mathcal S^\#$ by including the following formulas:
	\begin{itemize}
		\item $A^k\to A^{k\psi}$ for each atom $A$ occurring in $\mathcal S$, $k\in\Lambda$ and $\psi\in\mathcal F_\to$ not occurring in $k$.
		\item $A^k\to (B^k\circ C^k)$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^k\circ B^k)\to C^k$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^{k\psi}\to B^{k\psi})\to C^k$ for $\psi = (A\to B)\to C\in\mathcal S$, $k\in\Lambda$ if $\psi$ does not occurr in $k$.
	\end{itemize}
Then, $\bigwedge S\to P$ is intuitionistically valid iff $\bigwedge S^\#\to P^\epsilon$ is classically valid, where $\epsilon$ denotes the empty sequence. The size of $\mathcal S^\#$ is in $\mathcal O(|\mathcal S|\cdot2^{|\mathcal F_\to|\cdot\log(|\mathcal F_\to|)})$. Futhermore, there is an effective procedure for translating counter-models between the sentences.
\end{theorem}

@@

\begin{theorem}
	Let $\mathcal S$ be as in Theorem~\ref{thm:Tseytin} and $\mathcal F_\to\subseteq\mathcal S$ denote the subset of formulas of the form $(A\to B)\to C$. There is an effective procedure that produces a QBF $\varphi^Q$ of size $\mathcal O(|\mathcal S|\cdot|\mathcal F_\to| + |\mathcal F_\to|^3)$ with $2\cdot |\mathcal F_\to|-1$ quantifier alternations such that $\varphi$ is intuitionistically valid if and only if $\varphi^Q$ is not satisfiable. For fixed $N\in\mathbb N$, deciding intuitionistic validity for formulas $\bigwedge \mathcal S\to P$ where $\mathcal S$ is as above and $|\mathcal F_\to| = N$ is therefore in $\Sigma_{2N-1}$.
\end{theorem}

@@

We then move to the first-order case. Here the construction is a bit more involved but the underlying approach is the same.
Again we first perform a Tseytin-like transformation.
Here the non-classical content is encapsulated by formulas of type $(A\to B)\to C$ and $\forall xA\to B$.
The details of this translation are given in Section~\ref{section:tseytin}.
We then proceed similarly to the propositional case.
Note however that one difficulty arises from the fact that our (classical) domain will now contain on the one hand worlds in the Kripke frame but on the other hand also proper domain elements.
We resolve this apparent conflict by introducing a special binary predicate $E$, inspired by~\cite{iemhoff2010eskolemization}, encoding which domain elements exists at which world.
The main transformation then again proceeds in three steps:
Step 1) and 2) are analogous to the propositional case.
The real difference arises in step 3):
While we can also establish the existence of a canonic counter-model whose frame only depends on formulas of type $(A\to B)\to C$ and $\forall xA\to B$, the size of this counter-model is countably infinite in general.
This is not surprising since certain intuitionistically invalid formulas like the double negation shift $\forall x\neg\neg A(x)\to \neg\neg\forall x A(x)$ don't have finite counter-models.
Therefore we are not able to eliminate the $\forall$-quantifiers associated with the Kripke semantics.
However since our translation targets first-order logic, we believe that the introduction of these quantifiers is acceptable.
%
Summarizing, we obtain the following result:

@@

\begin{definition}
A $\Sigma$-\emph{Kripke structure} $\mathcal{K}$ is a partially ordered set $W$, called the Kripke \emph{frame}, and a family of $\Sigma$-structures $(\mathcal{M}_w)_{w\in W}$ such that for $u\leq w$ we have $M_u\subseteq M_w$, $f^{I_w}|_{M_u} = f^{I_u}$.\footnote{Here $f|_M$ denotes the restriction of $f$ to $M$} and $R^{I_w}|_{M_u} = R^{I_u}$.
	Then we define a model relation between worlds $u\in W$ and variable assignments $v$ (targeting $M_u$) and formulas $\varphi$ as follows:
	\begin{itemize}
		\item $u, v\not\models\bot$, $u, v\models R(t_1,\dots,t_n)$ iff $\mathcal M_u, v\models R(t_1,\dots,t_n)$, $u, v\models s = t$ iff $s^{I_u, v} = t^{I_u, v}$.
		\item $u, v\models \varphi\wedge \psi$ iff $u, v\models\varphi$ and $u, v\models\psi$, $u, v\models \varphi\vee\psi$ iff $u, v\models\varphi$ or $u, v\models\psi$.
		\item $u, v\models \varphi\to\psi$ iff for every $w\geq u$ we have $w, v\not\models\varphi$ or $w, v\models\psi$.
		\item $u, v\models\exists x\varphi$ iff there exists $m\in M_u$ such that $u, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $u, v\models\forall x\varphi$ iff for every $w\geq u$ and $m\in M_w$ we have $w, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\mathcal{K}$ satisfies $\varphi$ if $u, v\models\varphi$ holds for every world $u$ and variable assignment $v$. $\varphi$ is valid if it is satisfied by every Kripke structure.
$\varphi$ is valid for some frame (write $W\models\varphi$) if it is satisfied in every Krike structure with that frame. We denote the set of valid formulas with \emph{IQC} (Intuitionistic Quantified Calculus).
\end{definition}
In addition to the propositional tautologies there are now sentences involving quantifiers which are classically valid but not intuitionistically, e.g., $\neg\forall x A(x)\to \exists x \neg A(x)$.

@@

An important step in the embedding will be the elimination of quantifiers via Herbrandization.
In this process we introduce fresh variables and add additional function symbols to the signature.
A fresh variable is any variable that does not occur in any of the considered formulas.
Whenever we add a function symbol we implicitly extend the signature by some not previously contained symbol.

@@

\begin{definition}
	Let $\varphi$ be a propositional formula. Define $\varphi^{u}$ inductively as follows:
	\begin{itemize}
		\item $A^{u} = A(u)$ for every propositional variable $A$.
		\item $\bot^u = \bot$.
		\item $(\varphi\circ\psi)^u = \varphi^u\circ\psi^u$ for $\circ\in\{\wedge, \vee\}$.
		\item $(\varphi\to \psi)^u = \forall w(u\preceq w\to\varphi^{w}\to\psi^{w})$ where $w$ is some new variable.
	\end{itemize}
	Let $K(\varphi)$ encode the theory of Kripke structures, i.e.
	$$K(\varphi) = \text{\normalfont PartialOrder}(\preceq)\wedge\forall u\forall w(u\preceq w\to \text{\normalfont Persistent}(u, w))$$
	with e.g.
	\begin{align*}
		\text{\normalfont PartialOrder}(\preceq) =&\:\forall u(u\preceq u)\wedge\forall u\forall w(u\preceq w\to w\preceq u\to u = w)\wedge\\&\:\forall u\forall v\forall w(u\preceq v\to v\preceq w\to u\preceq w)\\
		\text{\normalfont Persistent}(u, w)=&\:\bigwedge \{A(u)\to A(w)\:|\: \text{ $A$ is a propositional variable that occurs in $\varphi$}\}
	\end{align*}
	Then define
	$$\varphi^{C} = K(\varphi)\to \varphi^{u}$$
	where $u$ is some free variable.
\end{definition}

@@

\begin{lemma}
	$\bigwedge S^+(\varphi)\wedge P_\varphi(\vec z_\varphi)\to\varphi$ and $\bigwedge S^-(\varphi)\wedge \varphi\to P_\varphi(\vec z_\varphi)$ are valid both classically and intuitionistically.
\end{lemma}

@@

\begin{lemma}\label{thm:struct2}
	For every structure $\mathcal M$,
	$\mathcal M\models \varphi$ if and only if $S(\mathcal M, \varphi)\models P_\varphi(\vec z_\varphi)$.
\end{lemma}

Then from the previous three Lemmata we get:

@@

Recall that since $\varphi$ is quantifier-free each formula $\psi\in\mathcal S^-(\varphi)$ is of one of the forms
$$A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C), (A\vee B)\to C, (A\to B)\to C,$$
where we can treat $A\to B$ as a special case $A\to (B\wedge B)$. We then apply the transformation to CQC, leading to a formula
$$\varphi'' = K(\varphi')\to\bigwedge  \mathcal S\to P_\varphi(u),$$
where $u$ is some new free variable and each $\psi\in\mathcal S$ is of one of the forms
$$\begin{matrix}
	\forall k(u\preceq k\to A(k)\to (B(k)\wedge C(k)))\indent  \forall k(u\preceq k\to (A(k)\wedge (B(k))\to C(k)))\\
	\forall k(u\preceq k\to A(k)\to (B(k)\vee C(k)))\indent \forall k(u\preceq k\to (A(k)\vee B(k))\to C(k))\\
	\forall k(u\preceq k\to (\forall l(k\preceq l \to A(l)\to B(l)))\to C(k)),
\end{matrix}$$
with each $P(x)$ possibly being $\bot$. Applying Herbrandization we obtain a formula
$$\varphi''' = K(\varphi')\to \bigwedge \mathcal S'\to P_\varphi(s),$$
where $s$ is some new constant term and each $\psi\in\mathcal S'$ is of one of the forms
$$\begin{matrix}
	\forall k(s\preceq k\to A(k)\to (B(k)\wedge C(k)))\indent \forall k(s\preceq k\to (A(k)\wedge (B(k))\to C(k)))\\
	\forall k(s\preceq k\to A(k)\to (B(k)\vee C(k)))\indent \forall k(s\preceq k\to (A(k)\vee (B(k))\to C(k)))\\
	\forall k(s\preceq k\to (k\preceq f_\psi(k) \to A(f_\psi(k))\to B(f_\psi(k)))\to C(k)),\\
\end{matrix}$$
and $f_\psi$ is a new function symbol for each introduced formula of that form. Now if $(M, I)$ is a counter-model, then we have a counter-model $(M',I')$ where $M' = \{m\in M|s\preceq m\}$ and
$f_\psi^{I'}(u) = f^I_\psi(u) \text{ iff $u\preceq f^{I}_\psi(u)$, and $f_\psi^{I'}(u) = u,$ else.}$ That is, where $s$ is the least element and the $f_\psi$ increase their argument. Therefore instead of $\varphi'''$ we may consider a formula $$\varphi^\circ = \forall k(s\preceq k)\to \bigwedge\{\forall k(k\preceq f_\psi(k))\:|\:\psi\in\mathcal F_\to\}\to K(\varphi')\to \bigwedge \mathcal S^\circ\to P_\varphi(s)$$ where each formula $\psi\in\mathcal S^\circ$ is of one of the forms
$$\begin{matrix}
	\forall k(A(k)\to (B(k)\wedge C(k)))\indent\forall k((A(k)\wedge B(k))\to C(k))\\
	\forall k(A(k)\to (B(k)\vee C(k)))\indent\forall k((A(k)\vee B_\psi(k))\to C(k))\\
	\forall k((A(f_\psi(k))\to B(f_\psi(k)))\to C(k)),
\end{matrix}$$
and $\mathcal F_\to$ denotes the set of formulas of the last kind.

@@

So we know that $\varphi^\circ$ is valid iff it is valid for structures that have as a domain the sequences without repetition over $\mathcal F_\to$, ordered by the prefix-relation and $$s^I = \epsilon, f_\psi^I(x) = \begin{cases}
	x, &\text{ if $\psi$ occurs in $x$,}\\
	x\psi, &\text{ otherwise.}
\end{cases}$$
Now we can replace every $\forall$-quantifier by enumerating all the ground terms, and then replace all distinct ground instances of relations by new propositional variables yielding a propositional formula. This gives us the translation stated in Theorem~\ref{thm:reduction-propositional}.
%\begin{theorem}
%	$\bigwedge\mathcal S\to P$ is intuitionistically valid iff $\bigwedge\mathcal S^\#\to P^\emptyset$ is classically valid.
%\end{theorem}

\begin{example}
	Let us consider the law of excluded middle $\varphi = A\vee\neg A$. Then we get
	$$\mathcal S^-(\varphi) = \{(P_A\vee P_{\neg A})\to P_\varphi, A\to P_A, (A\to \bot)\to P_{\neg A}\},$$
	and we know that $\varphi$ is valid iff $\bigwedge \mathcal S^-(\varphi)\to P_\varphi$ is valid. Applying the above lemma this is intuitionistically valid iff $\bigwedge\mathcal S^\#\to P^\emptyset_\varphi$ is classically valid, where, setting $\psi = (A\to \bot)\to P_{\neg A}$,
	\begin{align*}
		\mathcal S^\# =&\{P_\varphi^\epsilon\to P_\varphi^{\psi}, P_A^\epsilon\to P_A^{\psi},P_{\neg A}^\epsilon\to P_{\neg A}^{\psi},A^\epsilon\to A^{\psi}, (P_A^\epsilon\vee P_{\neg A}^\epsilon)\to P_\varphi^\epsilon, (P_A^{\psi}\vee P_{\neg A}^{\psi})\to P_\varphi^{\psi}\}\cup\\ &\{A^\epsilon\to P_A^\epsilon, P_A^{\psi}\to P_A^{\psi}, (A^{\psi}\to \bot)\to P_{\neg A}^\epsilon, (A^{\psi}\to \bot)\to P_{\neg A}^{\psi}\}.
	\end{align*}
	We now note that $P_\varphi^\epsilon  = P_A^\epsilon = P_{\neg A}^\epsilon = A^\epsilon = 0$, $P_{\varphi}^{\psi} = P_A^{\psi} =  P_{\neg A}^{\psi} = A^{\psi} = 1$ defines a counter-model.
\end{example}
